Forecasting Influenza Hospitalizations Using a Bayesian Hierarchical Nonlinear Model with Discrepancy

### 2025-12-01 CopyOfmanuscript_res.tex
fix section 3.7

This two-component modeling is remeniscent of the Bayesian cut 
described in \cite{plummer2015cuts} and \cite{nott2023bayesian}. Cutting a model
into two component models or ``modules`` may be justfied for several reasons
including to reduce time to fit the model, avoiding mixing issues of posterior
sampling distributions, improving predictive performance or to prevent
model misspecification in one model to influence the other 
\cite[]{nott2023bayesian, jacob2020unbiased, jacob2017better, plummer2015cuts}.

The decision to cut the forecast model into two component models
was made for several reasons.
When fitting the fully Bayesian joint model, the time to fit a single model using
Markov chain Monte Carlo (MCMC) sampling and
obtain forecasts was sometimes many hours whereas fitting the two models
separately took a fraction of the time. When assessing convergence of model
parameters, it was rare that posterior sampling chains for the joint model
showed convergence even after 55,000 iterations, whereas the component model 
fits gave no signs which raised concern for convergence. And most importantly,
the forecasts from the component models generally outperformed those of the 
joint model in terms of minimizing proper scoring rules.

@@

Model comparison was done by calculating a proper scoring rule for each 
forecast.
Proper scoring rules are the 
current standard for comparing performance between probabilistic forecasts 
and selecting the best forecasts according to the notion of maximizing 
sharpness subject to (auto-)calibration 
\cite[]{gneiting2007probabilistic, tsyplakov2013evaluation}. Proper scoring 
rules are commonly used in forecast comparison, and they are designed such 
that a 
forecaster is incentivized to be honest in the reporting of their forecasts 
\cite[]{gneiting2007strictly, gneiting2014probabilistic}.
The proper scoring rule primarily used in the FluSight competition and the 
COVID-19 Forecast Hub, and which is used in this simulation study,
is the negatively oriented
(smaller is better)
weighted interval score (WIS)
\cite[]{mathis2024evaluation, bracher2021evaluating}.
The WIS is used for scoring quantile or interval 
forecasts, or forecasts made up of predicitive intervals of several nominal 
levels
\cite[]{gneiting2007strictly, gneiting2014probabilistic, bracher2021evaluating}. 
The WIS defined in (\ref{eq:wis2}) where $Q$ is a forecast represented by all 
included quantiles, $B$ is the number of intervals,  $y^*$ is the observed 
value targeted by the forecast, $w_0 = 1/2$ and $w_b = \alpha_b / 2$ are 
weights for each interval, and $\alpha_b$ is the nominal level of the $b^{th}$ 
interval where $b \in \{1, ..., B\}$. 
$IS_{\alpha}$ is the interval score (IS), a proper scoring rule for a 
single interval, defined in (\ref{eq:is}). Here 
$\vmathbb{1}\{\cdot\}$ is the indicator function.

@@

For the
remainder of this section, focus will be made on forecasts made by coupling the
ASGD and SIRD models with the 
normal hospitalization model where ILI is a quadratic predictor.
These forecast schemes are denoted as ASGD\_NORM2 and SIRD\_NOMR2. 
In the supplementary materials, we include analysis of 2023 hospitalization
forecasts for several other forecast
models including ASG and SIR ILI models coupled with other variations of the
hospitalization model where the ASGD\_NORM2 showed the best results
and the SIRD\_NORM2 performed nearly as well as the ASGD\_NORM2.

The FluSight 
models which are used for comparison are the
20 non-ensemble models
submitted to FluSight during the 2023 season.
The submitted forecasts may be found at \cite{mathis2023flusight}.
Among the models
was the FluSight baseline. The baseline forecast had as a median the most 
recently observed 
hospitalization count, and the forecast uncertainty was based on 
differences between 
previous hospitalizations. The baseline forecast model was
similar to the baseline forecast model used in
previous flu forecasting seasons and in the COVID-19 hub 
\cite[]{mathis2024evaluation, Cramer2022-hub-dataset}.

Figure \ref{fig:lwis_cover_sum} shows forecast results for the 2023 flu 
hospitalization forecasts for all 22 models being compared but with results
for the ASGD\_NORM2, SIRD\_NORM2, and FluSight baseline models highlighted. 
For each week of the 2023 season, the  
LWIS averaged over location and horizon 
for each model is shown in a). Boxplots of LWIS for 1, 2, 3, and 4-week ahead
horizons for the ASGD\_NORM2, SIRD\_NORM2, and baseline models are shown in b). 
And 
overall empirical coverage of the 11 predictive intervals for all models is 
shown in c) with ASGD\_NORM2, SIRD\_NORM2
and the baseline model highlighted. 
These plots show that over the season the ASGD\_NORM2 model tended to 
outperform most others in terms of LWIS, and in general is superior to the 
baseline model. The coverage plot shows that the ASGD\_NORM2 model is well 
calibrated at most levels, with slight overcoverage at the lower levels
up to about 80\%, and has better coverage than all other models. Similar results
for the WIS are shown in the supplementary materials.

@@

    \centering
    % \begin{adjustwidth}{0cm}{0cm}
    \includegraphics[scale = .6]{Images/lwis_cover_sum.png}
    \caption{a) Log-weighted interval score (LWIS) averaged 
    over location and horizon for each week during the season for the 21 models being compared. 
    Each grey line represents one model, but the ASGD\_NORM2 (blue), 
    SIRD\_NORM2 (green), and 
    FluSight-baseline (red) are colored to stand out.
    b) Boxplots of all LWIS scores for 1, 2, 3, and 4-week ahead horizons 
    for the ASGD\_NORM2 (blue) and FluSight-baseline (red) models.
    c) Plot of empirical coverage against theoretical coverage for 11 
    predictive intervals from the 10\% nominal level to the 98\%. The black
    line $x = y$ shows where optimal coverage would fall.
    Each grey line represents one model, but the ASGD\_NORM2 (blue),
    SIRD\_NORM2 and 
    FluSight-baseline (red) are colored to stand out.}
    % \end{adjustwidth}
    \label{fig:lwis_cover_sum}
\end{figure}

During the FluSight competition, most participating teams would occasionally 
miss a forecast submission for some week, location, or horizon. This makes a 
simple average of scores an imperfect measure for comparison, as forecasts
of certain targets included for one model may be excluded by another model.
Thus in figure \ref{fig:state_and_date_lwis} 
the ASGD\_NORM2 model is compared with all 
other models individually using LWIS scores averaged over only the 
forecasts shared by the two models.
Each tile represents the ratio of average ASGD\_NORM2
LWIS to that of one FluSight model by location or by week.
We call this the relative LWIS (RLWIS). A value smaller than
1 indicates the ASGD\_NORM2 model outperforms the competing model. A value 
higher than 1 indicateds the ASGD\_NORM2 is outperformed. A grey tile indicates
the competing model had no forecasts matching the specified target.
Similar plots showing WIS scores are found in the supplementary materials. 
The ASGD\_NORM2 outperforms most other competing models more often than not, but
there are some weeks or locations where forecasting was poorer. For example, 
the plot shows the ASGD\_NORM2 performed poorly in Montana relative to most other
models.

Table \ref{tab:fin_analysis_stats} gives summary results for mean and median
WIS and LWIS scores, predictive coverage, and relative RWIS and RLWIS scores
for each model. Along with the plots in this section, it 
shows that over the course of the 
2023 season, 
the ASGD\_NORM2 outperformed every other model except the 
UGA\_flucast-INFLAenza. The SIRD\_NORM2 is also one of the top performing 
forecast models.

\begin{figure}[hbt!]
% \begin{adjustwidth}{-1.2cm}{-1.5cm}
    % \begin{minipage}{\linewidth}
    \centering
    \makebox[\linewidth][l]{
    \includegraphics[scale = .5]{Images/state_and_date_lwis.png}
    }
    % \end{adjustwidth}
    \caption{Ratio of average log-weighted interval score (LWIS) for ASGD\_NORM2 
    to that of each competing FluSight model. Scores are averaged
    over all targets within indicated location (top) or week (bottom) and 
    only include forecasts shared by both models. Lower scores (blue) indicate
    superior performance by the ASGD\_NORM2 model and higher scores (red)
    indicate superior performance by competing model.}
    \label{fig:state_and_date_lwis}
    % \end{minipage}

@@

\begin{table}[ht]
\centering
% \begin{adjustwidth}{-3cm}{-1.5cm}
\caption{Overall summary scores for each of the 20 non-ensemble FluSight
models and the ASGD\_NORM2 model. Summaries include mean weighted interval
and log-weighted interval scores (MWIS/MLWIS), 
median weighted interval and log-weighted interval scores (MedWIS/MedLWIS), 
mean squared error
difference between predictive model empirical and theoretical coverage (MSEC)
see figure \ref{fig:lwis_cover_sum} c)), percentage of forecasts for all 
targets during the 2023 season (\% Forcs), and relative weighted interval
and log-weighted interval scores (RWIS/RLWIS).}
\small
\begin{tabular}{lrrrrrrrr}
  % \hline
 & MWIS & MLWIS & MedWIS & MedLWIS & MSEC & \% Forcs & RWIS & RLWIS\\ 
  \hline
ASGD\_NORM2 & 62 & 0.34 & 14 & 0.23 & 0.001 & 100 & 1 & 1 \\ 
  PSI-PROF & 63 & 0.35 & 15 & 0.23 & 0.003 & 100 & 0.90 & 0.97 \\ 
  SIRD\_NORM2 & 67 & 0.36 & 16 & 0.26 & 0.001 & 100 & 0.93 & 0.95 \\
  CEPH-Rtrend\_fluH & 69 & 0.39 & 13 & 0.28 & 0.004 & 100 & 0.81 & 0.86 \\ 
  FluSight-baseline & 85 & 0.41 & 16 & 0.32 & 0.023 & 100 & 0.63 & 0.82 \\ 
  UM-DeepOutbreak & 83 & 0.46 & 21 & 0.39 & 0.010 & 99 & 0.64 & 0.72 \\ 
  cfarenewal-cfaepimlight & 76 & 0.37 & 15 & 0.26 & 0.001 & 99 & 0.72 & 0.92 \\ 
  MOBS-GLEAM\_FLUH & 66 & 0.35 & 15 & 0.22 & 0.021 & 98 & 0.87 & 0.95 \\ 
  LosAlamos\_NAU-CModel\_Flu & 242 & 0.64 & 24 & 0.42 & 0.153 & 93 & 0.21 & 0.53 \\ 
  UGuelph-CompositeCurve & 132 & 0.52 & 25 & 0.41 & 0.018 & 93 & 0.43 & 0.62 \\ 
  LUcompUncertLab-chimera & 84 & 0.43 & 17 & 0.33 & 0.004 & 92 & 0.67 & 0.71 \\ 
  UGA\_flucast-INFLAenza & 74 & 0.32 & 15 & 0.20 & 0.003 & 90 & 0.77 & 1.07 \\ 
  cfa-flumech & 101 & 0.41 & 17 & 0.27 & 0.019 & 89 & 0.58 & 0.85 \\ 
  UGA\_flucast-Copycat & 76 & 0.35 & 16 & 0.21 & 0.012 & 87 & 0.81 & 0.98 \\ 
  GT-FluFNP & 105 & 0.48 & 18 & 0.38 & 0.046 & 86 & 0.45 & 0.73 \\ 
  UNC\_IDD-InfluPaint & 107 & 0.35 & 16 & 0.24 & 0.043 & 78 & 0.58 & 0.95 \\ 
  NU\_UCSD-GLEAM\_AI\_FLUH & 98 & 0.39 & 22 & 0.24 & 0.014 & 74 & 0.68 & 0.83 \\ 
  SigSci-CREG & 59 & 0.49 & 12 & 0.31 & 0.018 & 71 & 0.62 & 0.74 \\ 
  PSI-PROF\_beta & 77 & 0.32 & 18 & 0.20 & 0.004 & 67 & 0.87 & 0.93 \\ 
  NIH-Flu\_ARIMA & 230 & 0.34 & 28 & 0.23 & 0.001 & 20 & 0.57 & 0.88 \\ 
  GH-model & 161 & 1.52 & 28 & 1.47 & 0.373 & 17 & 0.18 & 0.27 \\ 
  UGA\_flucast-OKeeffe & 27 & 0.59 & 8 & 0.43 & 0.003 & 10 & 0.60 & 0.58 \\  
\end{tabular}
% \end{adjustwidth}
\label{tab:fin_analysis_stats}
\end{table}

>>>>

This two-component modeling is remeniscent of the Bayesian cut 
described in \cite{plummer2015cuts} and \cite{nott2023bayesian}. Cutting a model
into two component models or ``modules`` may be justified for several reasons
including to reduce time to fit the model, avoiding mixing issues of posterior
sampling distributions, improving predictive performance or to prevent
model misspecification in one model to influence the other 
\cite[]{nott2023bayesian, jacob2020unbiased, jacob2017better, plummer2015cuts}.

The decision to cut the forecast model into two component models
was made for three major reasons.
When fitting the fully Bayesian joint model, the time to fit a single model using
Markov chain Monte Carlo (MCMC) sampling and
obtain forecasts was sometimes many hours whereas fitting the two models
separately took a fraction of the time. When assessing convergence of model
parameters, it was rare that posterior sampling chains for the joint model
showed convergence even after 55,000 iterations, whereas the component model 
fits gave no signs which raised concern for convergence. And most importantly,
the forecasts from the component models generally outperformed those of the 
joint model in terms of minimizing proper scoring rules.

@@

Model comparison was done by calculating a proper scoring rule for each 
forecast.
Proper scoring rules are the 
current standard for comparing performance between probabilistic forecasts 
and selecting the best forecasts according to the notion of maximizing 
sharpness subject to (auto-)calibration 
\cite[]{gneiting2007probabilistic, tsyplakov2013evaluation}. Proper scoring 
rules are commonly used in forecast comparison, and they are designed such 
that a 
forecaster is incentivized to be honest in the reporting of their forecasts 
\cite[]{gneiting2007strictly, gneiting2014probabilistic}.
Commonly used proper scoring rules for continuous distribution forecasts
include the log score and the continuously
ranked probability score (CRPS). 
The proper scoring rule primarily used in the FluSight competition and the 
COVID-19 Forecast Hub, and which is used in this simulation study,
is the negatively oriented
(smaller is better)
weighted interval score (WIS)
\cite[]{mathis2024evaluation, bracher2021evaluating}.
The WIS is used for scoring quantile or interval 
forecasts --the forecast format used in both FluSight and the 
COVID-19 Forecast Hub--
or forecasts made up of predicitive intervals of several nominal 
levels
\cite[]{gneiting2007strictly, gneiting2014probabilistic, bracher2021evaluating}. 
The WIS is 
defined in (\ref{eq:wis2}) where $Q$ is a forecast represented by all 
included quantiles, $B$ is the number of intervals,  $y^*$ is the observed 
value targeted by the forecast, $w_0 = 1/2$ and $w_b = \alpha_b / 2$ are 
weights for each interval, and $\alpha_b$ is the nominal level of the $b^{th}$ 
interval where $b \in \{1, ..., B\}$. 
$IS_{\alpha}$ is the interval score (IS), a proper scoring rule for a 
single interval, defined in (\ref{eq:is}). Here 
$\vmathbb{1}\{\cdot\}$ is the indicator function.
We note that as the number of forecast intervals $B$ increases, the WIS becomes 
arbitrarily close to
the CRPS. Thus, forecast scores under the CRPS and the WIS should be similar
\cite[]{bracher2021evaluating}.

@@

For the
remainder of this section, the focus is on forecasts made by coupling the
ASGD and SIRD models with the 
normal hospitalization model where ILI is a quadratic predictor.
These forecast schemes are denoted as ASGD\_NORM2 and SIRD\_NOMR2. 
In the supplementary materials, we include analysis of 2023 hospitalization
forecasts for several other forecast
models including ASG and SIR ILI models coupled with other variations of the
hospitalization model where the ASGD\_NORM2 showed the best results
and the SIRD\_NORM2 performed nearly as well as the ASGD\_NORM2.

During the FluSight competition, most participating teams would occasionally 
miss a forecast submission for some week, location, or horizon.
The FluSight 
models which are used for comparison are the
13 non-ensemble models which submitted forecasts for at least 80\% of 
FluSight targets during the 2023 season. 
The submitted forecasts may be found at \cite{mathis2023flusight}.
Among the models
was the FluSight baseline. The baseline forecast had as a median the most 
recently observed 
hospitalization count, and the forecast uncertainty was based on 
differences between 
previous hospitalizations. The baseline forecast model was
similar to the baseline forecast model used in
previous flu forecasting seasons and in the COVID-19 hub 
\cite[]{mathis2024evaluation, Cramer2022-hub-dataset}.

Figure \ref{fig:lwis_cover_sum} shows forecast results for the 2023 flu 
hospitalization forecasts for all 15 models being compared but with results
for the ASGD\_NORM2, SIRD\_NORM2, and FluSight baseline models highlighted. 
For each week of the 2023 season, the  
LWIS averaged over location and horizon 
for each model is shown in a). Boxplots of LWIS for 1, 2, 3, and 4-week ahead
horizons for the ASGD\_NORM2, SIRD\_NORM2, and baseline models are shown in b). 
And 
overall empirical coverage of the 11 predictive intervals for all models is 
shown in c) with ASGD\_NORM2, SIRD\_NORM2
and the baseline model highlighted. 
These plots show that over the season the ASGD\_NORM2 model tended to 
outperform most others in terms of LWIS, and in general is superior to the 
baseline model. The coverage plot shows that the ASGD\_NORM2 model is well 
calibrated at most levels, with slight overcoverage at the lower levels
up to about 80\%, and has better coverage than all other models. Similar results
for the WIS are shown in the supplementary materials.

@@

    \centering
    % \begin{adjustwidth}{0cm}{0cm}
    \includegraphics[scale = .6]{Images/lwis_cover_sum2.png}
    \caption{a) Log-weighted interval score (LWIS) averaged 
    over location and horizon for each week during the season for the 21 models being compared. 
    Each grey line represents one model, but the ASGD\_NORM2 (blue), 
    SIRD\_NORM2 (green), and 
    FluSight-baseline (red) are colored to stand out.
    b) Boxplots of all LWIS scores for 1, 2, 3, and 4-week ahead horizons 
    for the ASGD\_NORM2 (blue) and FluSight-baseline (red) models.
    c) Plot of empirical coverage against theoretical coverage for 11 
    predictive intervals from the 10\% nominal level to the 98\%. The black
    line $x = y$ shows where optimal coverage would fall.
    Each grey line represents one model, but the ASGD\_NORM2 (blue),
    SIRD\_NORM2 and 
    FluSight-baseline (red) are colored to stand out.}
    % \end{adjustwidth}
    \label{fig:lwis_cover_sum}
\end{figure}

Because forecast submissions for some targets were occassionally missed
by participating teams, for any two models there was often a mismatch between
targets for which forecasts were included or exlcuded. This makes a
simple average of scores is an imperfect measure for comparison.
Thus in figure \ref{fig:state_and_date_lwis}, 
the ASGD\_NORM2 model is compared with all 
other models individually using LWIS scores averaged over only the 
forecasts shared by the two models.
Each tile represents the ratio of average ASGD\_NORM2
LWIS to that of one FluSight model by location or by week.
We call this the relative LWIS (RLWIS). A value smaller than
1 indicates the ASGD\_NORM2 model outperforms the competing model. A value 
higher than 1 indicateds the ASGD\_NORM2 is outperformed. A grey tile indicates
the competing model had no forecasts matching the specified target.
Similar plots showing WIS scores are found in the supplementary materials. 
The ASGD\_NORM2 outperforms most other competing models more often than not, but
there are some weeks or locations where forecasting was poorer. For example, 
the plot shows the ASGD\_NORM2 performed poorly in Montana relative to most other
models.

Table \ref{tab:fin_analysis_stats} gives the numerical values for RLWIS 
and relative WIS (RWIS) over
all locations and weeks for each model, relative to the ASGD\_NORM2 model.
It also includes the non relative mean WIS and LWIS for each model, that is the 
overall mean scores for all forecasts submitted regardless of submission overlap
with another model.
Along with the plots in this section, it 
shows that over the course of the 
2023 season, 
the ASGD\_NORM2 outperformed every other model except the 
UGA\_flucast-INFLAenza. The SIRD\_NORM2 is also one of the top performing 
forecast models.

\begin{figure}[hbt!]
% \begin{adjustwidth}{-1.2cm}{-1.5cm}
    % \begin{minipage}{\linewidth}
    \centering
    \makebox[\linewidth][l]{
    \includegraphics[scale = .5]{Images/state_and_date_lwis2.png}
    }
    % \end{adjustwidth}
    \caption{Ratio of average log-weighted interval score (LWIS) for ASGD\_NORM2 
    to that of each competing FluSight model. Scores are averaged
    over all targets within indicated location (top) or week (bottom) and 
    only include forecasts shared by both models. Lower scores (blue) indicate
    superior performance by the ASGD\_NORM2 model and higher scores (red)
    indicate superior performance by competing model.}
    \label{fig:state_and_date_lwis}
    % \end{minipage}

@@

\begin{table}[ht]
\centering
% \begin{adjustwidth}{-3cm}{-1.5cm}
\caption{Overall summary scores for each of the 13 non-ensemble FluSight
models with over 80\% submissions and 
the ASGD\_NORM2 and SIRD\_NORM2 models.
Summaries include 
mean weighted interval the relative log-weighted interval
and weighted interval scores (RLWIS/RWIS),
the overall mean log-weighted and weighted interval scores (MLWIS/MWIS), 
mean squared error
difference between predictive model empirical and theoretical coverage (MSEC)
see figure \ref{fig:lwis_cover_sum} c)), and percentage of forecasts 
submitted for all 
targets during the 2023 season (\% Forcs).}
\small
\begin{tabular}{lrrrrrrrr}
  % \hline
                              & RLWIS & RWIS & MLWIS & MWIS & MSEC  & \% Forcs\\ 
  \hline 
  ASGD\_NORM2                 & 1     & 1    & 0.34  & 62   & 0.001 & 100 \\ 
  PSI-PROF                    & 0.98  & 0.98 & 0.35  & 63   & 0.003 & 100 \\ 
  SIRD\_NORM2                 & 0.95  & 0.93 & 0.36  & 67   & 0.001 & 100 \\ 
  CEPH-Rtrend\_fluH           & 0.87  & 0.89 & 0.39  & 69   & 0.004 & 100 \\ 
  FluSight-baseline           & 0.83  & 0.73 & 0.41  & 85   & 0.023 & 100 \\ 
  UM-DeepOutbreak             & 0.74  & 0.73 & 0.46  & 83   & 0.010 & 99 \\ 
  cfarenewal-cfaepimlight     & 0.93  & 0.82 & 0.37  & 76   & 0.001 & 99 \\ 
  MOBS-GLEAM\_FLUH            & 0.97  & 0.95 & 0.35  & 66   & 0.021 & 98 \\ 
  LosAlamos\_NAU-CModel\_Flu  & 0.54  & 0.26 & 0.64  & 242  & 0.153 & 93 \\ 
  UGuelph-CompositeCurve      & 0.66  & 0.50 & 0.52  & 132  & 0.018 & 93 \\ 
  LUcompUncertLab-chimera     & 0.73  & 0.76 & 0.43  & 84   & 0.004 & 92 \\ 
  UGA\_flucast-INFLAenza      & 1.09  & 0.90 & 0.32  & 74   & 0.003 & 90 \\ 
  cfa-flumech                 & 0.86  & 0.65 & 0.41  & 101  & 0.019 & 89 \\ 
  UGA\_flucast-Copycat        & 0.99  & 0.89 & 0.35  & 76   & 0.012 & 87 \\ 
  GT-FluFNP                   & 0.74  & 0.56 & 0.48  & 105  & 0.046 & 86 \\ 
  % UNC\_IDD-InfluPaint         & 107 & 0.35 & 16 & 0.24 & 0.043 & 78 & 0.58 & 0.95 \\ 
  % NU\_UCSD-GLEAM\_AI\_FLUH    & 98 & 0.39 & 22 & 0.24 & 0.014 & 74 & 0.68 & 0.83 \\ 
  % SigSci-CREG                 & 59 & 0.49 & 12 & 0.31 & 0.018 & 71 & 0.62 & 0.74 \\ 
  % PSI-PROF\_beta              & 77 & 0.32 & 18 & 0.20 & 0.004 & 67 & 0.87 & 0.93 \\ 
  % NIH-Flu\_ARIMA              & 230 & 0.34 & 28 & 0.23 & 0.001 & 20 & 0.57 & 0.88 \\ 
  % GH-model                    & 161 & 1.52 & 28 & 1.47 & 0.373 & 17 & 0.18 & 0.27 \\ 
  % UGA\_flucast-OKeeffe        & 27 & 0.59 & 8 & 0.43 & 0.003 & 10 & 0.60 & 0.58 \\  
\end{tabular}
% \end{adjustwidth}
\label{tab:fin_analysis_stats}
\end{table}

\begin{table}[ht]
\centering
% \begin{adjustwidth}{-3cm}{-1.5cm}
\caption{Overall summary scores for each of the 13 non-ensemble FluSight
models with over 80\% submissions and 
the ASGD\_NORM2 and SIRD\_NORM2 models. 
Summaries include mean weighted interval
and log-weighted interval scores (MWIS/MLWIS), 
mean squared error
difference between predictive model empirical and theoretical coverage (MSEC)
see figure \ref{fig:lwis_cover_sum} c)), percentage of forecasts for all 
targets during the 2023 season (\% Forcs), and relative weighted interval
and log-weighted interval scores (RWIS/RLWIS).
\\}
\small
\begin{tabular}{lrrrrrrrr}
  % \hline
                              & MWIS & MLWIS & MSEC  & \% Forcs & RWIS & RLWIS\\ 
  \hline 
ASGD\_NORM2                   & 62   & 0.34  & 0.001 & 100      & 1    & 1 \\ 
  PSI-PROF                    & 63   & 0.35  & 0.003 & 100      & 0.90 & 0.97 \\ 
  SIRD\_NORM2                 & 67   & 0.36  & 0.001 & 100      & 0.93 & 0.95 \\
  CEPH-Rtrend\_fluH           & 69   & 0.39  & 0.004 & 100      & 0.81 & 0.86 \\ 
  FluSight-baseline           & 85   & 0.41  & 0.023 & 100      & 0.63 & 0.82 \\ 
  UM-DeepOutbreak             & 83   & 0.46  & 0.010 & 99       & 0.64 & 0.72 \\ 
  cfarenewal-cfaepimlight     & 76   & 0.37  & 0.001 & 99       & 0.72 & 0.92 \\ 
  MOBS-GLEAM\_FLUH            & 66   & 0.35  & 0.021 & 98       & 0.87 & 0.95 \\ 
  LosAlamos\_NAU-CModel\_Flu  & 242  & 0.64  & 0.153 & 93       & 0.21 & 0.53 \\ 
  UGuelph-CompositeCurve      & 132  & 0.52  & 0.018 & 93       & 0.43 & 0.62 \\ 
  LUcompUncertLab-chimera     & 84   & 0.43  & 0.004 & 92       & 0.67 & 0.71 \\ 
  UGA\_flucast-INFLAenza      & 74   & 0.32  & 0.003 & 90       & 0.77 & 1.07 \\ 
  cfa-flumech                 & 101  & 0.41  & 0.019 & 89       & 0.58 & 0.85 \\ 
  UGA\_flucast-Copycat        & 76   & 0.35  & 0.012 & 87       & 0.81 & 0.98 \\ 
  GT-FluFNP                   & 105  & 0.48  & 0.046 & 86       & 0.45 & 0.73 \\ 
  % UNC\_IDD-InfluPaint         & 107 & 0.35 & 16 & 0.24 & 0.043 & 78 & 0.58 & 0.95 \\ 
  % NU\_UCSD-GLEAM\_AI\_FLUH    & 98 & 0.39 & 22 & 0.24 & 0.014 & 74 & 0.68 & 0.83 \\ 
  % SigSci-CREG                 & 59 & 0.49 & 12 & 0.31 & 0.018 & 71 & 0.62 & 0.74 \\ 
  % PSI-PROF\_beta              & 77 & 0.32 & 18 & 0.20 & 0.004 & 67 & 0.87 & 0.93 \\ 
  % NIH-Flu\_ARIMA              & 230 & 0.34 & 28 & 0.23 & 0.001 & 20 & 0.57 & 0.88 \\ 
  % GH-model                    & 161 & 1.52 & 28 & 1.47 & 0.373 & 17 & 0.18 & 0.27 \\ 
  % UGA\_flucast-OKeeffe        & 27 & 0.59 & 8 & 0.43 & 0.003 & 10 & 0.60 & 0.58 \\  
\end{tabular}
% \end{adjustwidth}
\label{tab:fin_analysis_stats}
\end{table}

% \begin{table}[ht]
% \centering
% % \begin{adjustwidth}{-3cm}{-1.5cm}
% \caption{Overall summary scores for each of the 13 non-ensemble FluSight
% models with over 80\% submissions and 
% the ASGD\_NORM2 and SIRD\_NORM2 models. 
% Summaries include mean weighted interval
% and log-weighted interval scores (MWIS/MLWIS), 
% median weighted interval and log-weighted interval scores (MedWIS/MedLWIS), 
% mean squared error
% difference between predictive model empirical and theoretical coverage (MSEC)
% see figure \ref{fig:lwis_cover_sum} c)), percentage of forecasts for all 
% targets during the 2023 season (\% Forcs), and relative weighted interval
% and log-weighted interval scores (RWIS/RLWIS).}
% \small
% \begin{tabular}{lrrrrrrrr}
%   % \hline
%                               & MWIS & MLWIS & MedWIS & MedLWIS & MSEC  & \% Forcs & RWIS & RLWIS\\ 
%   \hline 
% ASGD\_NORM2                   & 62   & 0.34  & 14     & 0.23    & 0.001 & 100      & 1    & 1 \\ 
%   PSI-PROF                    & 63   & 0.35  & 15     & 0.23    & 0.003 & 100      & 0.90 & 0.97 \\ 
%   SIRD\_NORM2                 & 67   & 0.36  & 16     & 0.26    & 0.001 & 100      & 0.93 & 0.95 \\
%   CEPH-Rtrend\_fluH           & 69   & 0.39  & 13     & 0.28    & 0.004 & 100      & 0.81 & 0.86 \\ 
%   FluSight-baseline           & 85   & 0.41  & 16     & 0.32    & 0.023 & 100      & 0.63 & 0.82 \\ 
%   UM-DeepOutbreak             & 83   & 0.46  & 21     & 0.39    & 0.010 & 99       & 0.64 & 0.72 \\ 
%   cfarenewal-cfaepimlight     & 76   & 0.37  & 15     & 0.26    & 0.001 & 99       & 0.72 & 0.92 \\ 
%   MOBS-GLEAM\_FLUH            & 66   & 0.35  & 15     & 0.22    & 0.021 & 98       & 0.87 & 0.95 \\ 
%   LosAlamos\_NAU-CModel\_Flu  & 242  & 0.64  & 24     & 0.42    & 0.153 & 93       & 0.21 & 0.53 \\ 
%   UGuelph-CompositeCurve      & 132  & 0.52  & 25     & 0.41    & 0.018 & 93       & 0.43 & 0.62 \\ 
%   LUcompUncertLab-chimera     & 84   & 0.43  & 17     & 0.33    & 0.004 & 92       & 0.67 & 0.71 \\ 
%   UGA\_flucast-INFLAenza      & 74   & 0.32  & 15     & 0.20    & 0.003 & 90       & 0.77 & 1.07 \\ 
%   cfa-flumech                 & 101  & 0.41  & 17     & 0.27    & 0.019 & 89       & 0.58 & 0.85 \\ 
%   UGA\_flucast-Copycat        & 76   & 0.35  & 16     & 0.21    & 0.012 & 87       & 0.81 & 0.98 \\ 
%   GT-FluFNP                   & 105  & 0.48  & 18     & 0.38    & 0.046 & 86       & 0.45 & 0.73 \\ 
%   % UNC\_IDD-InfluPaint         & 107 & 0.35 & 16 & 0.24 & 0.043 & 78 & 0.58 & 0.95 \\ 
%   % NU\_UCSD-GLEAM\_AI\_FLUH    & 98 & 0.39 & 22 & 0.24 & 0.014 & 74 & 0.68 & 0.83 \\ 
%   % SigSci-CREG                 & 59 & 0.49 & 12 & 0.31 & 0.018 & 71 & 0.62 & 0.74 \\ 
%   % PSI-PROF\_beta              & 77 & 0.32 & 18 & 0.20 & 0.004 & 67 & 0.87 & 0.93 \\ 
%   % NIH-Flu\_ARIMA              & 230 & 0.34 & 28 & 0.23 & 0.001 & 20 & 0.57 & 0.88 \\ 
%   % GH-model                    & 161 & 1.52 & 28 & 1.47 & 0.373 & 17 & 0.18 & 0.27 \\ 
%   % UGA\_flucast-OKeeffe        & 27 & 0.59 & 8 & 0.43 & 0.003 & 10 & 0.60 & 0.58 \\  
% \end{tabular}
% % \end{adjustwidth}
% \label{tab:fin_analysis_stats}
% \end{table}
